---
title: "HW_2_Patutina"
author: "Patutina Ekaterina, 175"
date: "2/12/2021"
output: pdf_document
---
## Assignment 1,2
```{r}
library(network)
drugpaj <- read.paj('drugnet2.paj')
drug <- drugpaj$networks[[1]] # Extract network
plot(drug)
#check what attributes we have and lets extract them
names(drugpaj$partitions)
gender <- drugpaj$partitions[[1]]
ethnicity <- drugpaj$partitions[[2]]
drug <-set.vertex.attribute(drug, 'gender', value=c(gender))
drug <-set.vertex.attribute(drug, 'ethnicity', value=c(ethnicity))
gender <- drugpaj$partitions[[1]]
colors1 <- ifelse(gender == 1,'cadetblue' , ifelse(gender == 2, 'indianred', 'grey'))
plot(drug, vertex.col = colors1)

colors2 <- ifelse(ethnicity ==1,'grey' , ifelse(ethnicity == 2, 'indianred', ifelse(ethnicity == 0,'green','cadetblue')))
plot(drug, vertex.col = colors2)

```
As a result we see that men are more prone to be in the center of the network.
And what is more interesting people of one ethnicity are more prone to have deals with their ethnicity. There are 2 big clusters, and both of them have ethnicity majority, but ethnicity are different.

## Assignment 3
```{r}
load('madmen.Rdata')
mad.net <- as.network(mad.matrix, directed=FALSE)
set.vertex.attribute(mad.net,attrname='female', value=mad.att[,2])
coordkk<-network.layout.kamadakawai(mad.net,mad.att)
plot(mad.net, coord = coordkk)
coordfr<-network.layout.fruchtermanreingold(mad.net,mad.att)
plot(mad.net, coord = coordfr)
coordcr<-network.layout.circle(mad.net,mad.att)
edge_number = c()
for (i in 1:length(mad.matrix[,1])) {
  tmp = 0
  tmp = sum(c(mad.matrix[,i]))
  tmp = sqrt(tmp) + 1
  edge_number = c(edge_number, tmp)
}
if_female= ifelse(mad.att$Female == 1, 'pink', 'blue')
```

```{r,fig.align='center', size=500}
plot(mad.net, vertex.cex=2, vertex.col = if_female, coord = coordfr, 
     displaylabels=TRUE, label.cex=0.5, main = "The sexual network of the TV show 'Mad Men'")
plot(mad.net, vertex.cex=edge_number, vertex.col = if_female, coord = coordfr, 
     displaylabels = TRUE, label.cex = 0.5, main = "The sexual network of the TV show 'Mad Men'")
```
## Assignment 4
```{r}
library(igraph)
load('trade.Rdata')
trade.all<-as.matrix(trade.all)
trade_1 <- ifelse(trade.all > 0, 1, 0)
trade_2 <- ifelse(trade.all > 1, 1, 0)
trade_3 <- ifelse(trade.all > 2, 1, 0)
trade_4 <- ifelse(trade.all > 3, 1, 0)
trade_5 <- ifelse(trade.all > 4, 1, 0)
tradegraph_1 <-graph.adjacency(trade_1,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
tradegraph_2 <-graph.adjacency(trade_2,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
tradegraph_3 <-graph.adjacency(trade_3,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
tradegraph_4 <-graph.adjacency(trade_4,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
tradegraph_5 <-graph.adjacency(trade_5,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
coord_new = layout.fruchterman.reingold(tradegraph_1)
plot(tradegraph_1, vertex.size = 8, layout=coord_new, edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
plot(tradegraph_2, vertex.size = 8, layout=coord_new, edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
plot(tradegraph_3, vertex.size = 8, layout=coord_new,edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
plot(tradegraph_4, vertex.size = 8, layout=coord_new,edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
plot(tradegraph_5, vertex.size = 8, layout=coord_new,edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
x = c(sum(trade_1), sum(trade_2), sum(trade_3), sum(trade_4), sum(trade_5))
y = c(1,2,3,4,5)
plot(x,y)
```


#Lost ties for at least four ties network


```{r}
trade_4_1_full = trade_4 + trade_1
trade_4_1 <- ifelse(trade_4_1_full == 1, 1, 0)
tradegraph_4_1 <-graph.adjacency(trade_4_1,
mode=c("directed"),
weighted=NULL,
diag=FALSE)
plot(tradegraph_4_1, vertex.size = 8, layout=coord_new,edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
```


#How would you justify any of these choices? What are the impirical implication of these choices?


Decrease of the necessary number of the ties by one leads to increase of the number of directed ties by somewhat about 100. The largest increase is between 5 and 4 necessary nodes. Probably, it is a good idea to work with 4 necessary nodes. When we use model with 4 nodes, we still have quite a lot of ties - 219 (for 24 countries, max possible number of directed ties is 552).

#What differences do you observe between the graphs where the cutpoint is any tie, at least two ties, and all ties present?


Decrease of the number of ties. But anyway countries who has largest number of ties. Still have largest number of ties.
```{r}
edge_number_1 = c()
edge_number_2 = c()
edge_number_3 = c()
edge_number_4 = c()
edge_number_5 = c()
for (i in 1:length(trade_1[,1])) {
  tmp = sum(c(trade_1[,i]))
  edge_number_1 = c(edge_number_1, tmp)
  tmp = sum(c(trade_2[,i]))
  edge_number_2 = c(edge_number_2, tmp)
  tmp = sum(c(trade_3[,i]))
  edge_number_3 = c(edge_number_3, tmp)
  tmp = sum(c(trade_4[,i]))
  edge_number_4 = c(edge_number_4, tmp)
  tmp = sum(c(trade_5[,i]))
  edge_number_5 = c(edge_number_5, tmp)
}
edge_number_1
edge_number_3
edge_number_5
plot(edge_number_1, edge_number_3)
plot(edge_number_1, edge_number_4)
plot(edge_number_1, edge_number_5)
all = cbind(edge_number_1, edge_number_2, edge_number_3, edge_number_4, edge_number_5)
all
```
## Assignment 5
```{r}
food_graph <-graph.adjacency(as.matrix(food),
mode=c("directed"),
weighted=NULL,
diag=FALSE)
plot(food_graph, vertex.size = 8, edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
plot(food_graph, vertex.size = 8, layout=coord_new, edge.arrow.size = .2, vertex.label.cex = .5,
vertex.color = 'cadetblue', edge.color='pink', vertex.label.dist = 1.5, vertex.label.color = 'black')
sum(food)
#about half of all possible ties are food ties
food_ties = c()
for (i in 1:length(as.matrix(food[,1]))) {
  tmp = 0
  tmp = sum(as.matrix(food)[,i])
  food_ties = c(food_ties, tmp)
}
names(food)
food_top = as.matrix(cbind(names(food), food_ties, all))
food_top
plot(edge_number_1, food_ties)
plot(edge_number_4, food_ties)
```
